---
title: "Lab 00 - Hello IDS!"
author: "Kieran Lewis"
date: "`r Sys.Date()`"
output: html_document
---

### Load packages and data

```{r load-packages, message=FALSE}
library(tidyverse) 
```

### Exercises 16-17

We set up the data frame. Edit the data below to include information about your team members.

```{r setup-tibble}
team_data <- tibble(
  name = c("Kieran", "Luke", "Lee", 
           "member 3", "member 4"),
  github_username = c("KLewis144", "Luke-Hardwick", "liyifu123", 
                      "username 3", "username 4"), 
  colour = c("purple2", "orange", "blue", 
             "colour 3", "colour 4"),
  hobby = c("Guitar", "Bass Guitar", "Badminton", 
            "hobby 3", "hobby 4"),
  favourite_number = c(7, 6, 8, NA, NA)
  )

team_data
```

### Exercise 18

We now work on visualising our data. 

```{r bar-plot}
p1 <- ggplot(data = team_data, 
             mapping = aes(x = github_username, 
                           y = favourite_number,
                           fill = colour), 
             ) +
   geom_col() +
   scale_fill_identity()
p1
```


The plot shows a bar chart detailing the favourite numbers of everyone in the team

### Exercises 19

Change the text of the plot title and axis labels.

```{r labelled-bar-plot}
p1 + labs(x = "Person", 
          y = "Favourite Number",
          title = "Favourite numbers of the team")
```

The command labs() allows you to label the axis and title of the graph

### Exercise 20

```{r new-bar-plot}
p2 <- ggplot(team_data, aes(x = hobby)) +
  geom_bar()
p2
```

A pie chart would most likely be a better way of displaying this
